---
title: "Alcohol vs Seat choice"
author: "Nathan Abromovich"
date: "Fall 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

Visually it appears that the back row is quite different than middle rows. With the biggest difference shown between the back and front rows.  

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The data shows that the back row drink the most at 8.5 drinks a week while the front only drinks 1.7 per week and the middle row partakes in 3.3 drinks per week. With the data in hand we can show that they are not drinking the same amount per week.  



## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The p value shows the chances of getting a result that we obtained if the null hypothesis is true.  Since the result is so small I am rejecting the null hypothesis. 

We now need to look to see if we can find what is different from what? 
```{r}
plot(TukeyHSD(model1))
```
This shows that the the middle back and front back has differences while the middle and front appear to have no differences. 


## Conclusions
In conclusion we found out that there were three different categories so a one way Anova had to be run.  This showed that two of the rows are the same while the back row was different.  That data shows that the drunks occupy the back row in the room. 

