---
title: "Alcohol vs Seat choice"
author: "Nathan Abromovich"
date: "Fall 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

Visually it appears that the back row is quite different than middle rows. With the biggest difference shown between the back and front rows.  

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```

The data shows that the back row drink the most at 8.5 drinks a week while the front only drinks 1.7 per week and the middle row partakes in 3.3 drinks per week. With the data in hand we can show that they are not drinking the same amount per week.  



## Inferential Tests

## Conclusions


